### 2018-09-16 Sections/cryptowars.tex
references for QKD added

\subsection{Trojan horse attack}
The family of Trojan horse attacks involves Eve probing the settings of Alice and Bob by
sending light into their devices and collecting the reflected signal. 
The first one of this kind of attacks actually came for free for the eavesdropper \cite{}: it was discovered that some photon counters emits light when a photon was detected \cite{}. If the emitted light carries information on which detector was triggered, it must be prevented to leak out.

@@

Ref.~\cite{PhysRevLett.68.3121}

@@

If the state preparation consists of more than one photon, Eve can count the number of photons in each signal and act accordingly. Such attacks are called photon-number splitting (PNS) attacks. The BS and PNS attacks were discovered as zero-error attacks against BB84 implemented with a weak laser pulses. To counter the attack, the decoy-state method\cite{} method was developed.

@@

Eve can also go behond detector blinding. She can send in a powerful laser pulse to optically damage component in the QKD system and permanently change its characteristics\cite{}. If the new characteristics then assist the eavesdropper in an attack without Alice or Bob being notified, the security of that practical QKD system would be severly compromised.
% 
% 
A more detailed discussion on attacks on the physical implementation can be found in Ref.~\cite{}.

>>>>

\subsection{Trojan horse attack}
The family of Trojan horse attacks involves Eve probing the settings of Alice and Bob by
sending light into their devices and collecting the reflected signal. 
The first one of this kind of attacks actually came for free for the eavesdropper \cite{RevModPhys.81.1301}: it was discovered that some photon counters emits light when a photon was detected \cite{kurtsiefer2001breakdown}. If the emitted light carries information on which detector was triggered, it must be prevented to leak out.

@@

@@

If the state preparation consists of more than one photon, Eve can count the number of photons in each signal and act accordingly. Such attacks are called photon-number splitting (PNS) attacks \cite{PhysRevLett.68.3121}. The BS and PNS attacks were discovered as zero-error attacks against BB84 implemented with a weak laser pulses. To counter the attack, the decoy-state method\cite{PhysRevLett.91.057901, PhysRevLett.94.230504} method was developed.

@@

Eve can also go behond detector blinding. She can send in a powerful laser pulse to optically damage component in the QKD system and permanently change its characteristics \cite{jain2016attacks}. If the new characteristics then assist the eavesdropper in an attack without Alice or Bob being notified, the security of that practical QKD system would be severly compromised.
% 
% 
A more detailed discussion on attacks on the physical implementation can be found in Ref.~\cite{jain2016attacks}.
